Brother, Can You Spare a Manufacturing Job?  How Voters React to Deindustrialization

### 2021-12-13 Final Draft/Final Draft.Rmd
more language changes

A potential weakness of our first approach is that manufacturing employment may be correlated with swinging towards Trump for reasons other than manufacturing job losses. To account for this potential ommitted variable bias, we use a second approach that attempts to balance the covariates of the deindustrialization treatment. We use the same covariates as are used in controls above, as well as manufacturing as share of the population and total population. We apply the method of Covariate Balancing Propensity Scores, as developed by \cite{Imai14}; this method generates weights to reduce the correlation between covariates and treatment, while addressing several of the issues with propensity score weights. We find significant imbalance in the data - in other words, it is relatively easy to predict the 'treatment' of job loss given the covariates (see Appendix for balance plots). Given covariate-balancing weights, we then conduct a single-stage weighted regression of change in Democratic vote share on manufacturing job loss, using the same controls as above. Essentially, this approach can be conceptualized as a form of matching that reduces the potential ommitted variable bias in our first approach, but may introduce selection bias (as some counties will be given low weights).

@@

We find that counties experiencing deindustrialization from 2004-2015 are substantially more likely to vote for Trump. Further, we find that this effect is largely attributable to whites. In other words, net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased Democratic vote share. We find the same effect when using covariate balancing, albeit of reduced size.

>>>>

A potential weakness of our first approach is that manufacturing employment may be correlated with swinging towards Trump for reasons other than manufacturing job losses. To account for this potential ommitted variable bias, we use a second approach that attempts to balance the covariates of the deindustrialization treatment. We use the same covariates as are used in controls above, as well as manufacturing as share of the population and total population. We apply the method of Covariate Balancing Propensity Scores, as developed by \cite{Imai14}; this method generates weights to reduce the correlation between covariates and treatment, while addressing several of the issues with propensity score weights. We find significant imbalance in the data - in other words, it is relatively easy to predict the 'treatment' of job loss given the covariates (see Figures \ref{balPlot} and \ref{balPlotWhite} for balance plots). Given covariate-balancing weights, we then conduct a single-stage weighted regression of change in Democratic vote share on manufacturing job loss, using the same controls as above. Essentially, this approach can be conceptualized as a form of matching that reduces the potential ommitted variable bias in our first approach, but may introduce selection bias (as some counties will be given low weights).

@@

We find that counties experiencing deindustrialization from 2004-2015 are substantially more likely to vote for Trump. Further, we find that this effect is largely attributable to whites. In other words, net white manufacturing job losses decreased Democratic vote share, while net non-white manufacturing job losses increased Democratic vote share. We find the same effect when using covariate balancing, albeit of reduced size (we are investigating the difference in magnitude).
